Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.

### 2016-10-02 paper_intersections.tex
New plots for the scaling benchmark.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.8\textwidth]{\figpath intersections_test1_cube_speed_scaling.pdf}
    \caption{Dependence of the algorithms performance on number of intersection (and mesh refinement). }
    \label{fig:cube_speed}
\end{figure}

>>>>

\begin{figure}[!htb]
    \centering
    \includegraphics[width=1.0\textwidth]{\figpath cube_scale.pdf}
    \caption{Time complexity for the initialization phase (left) with respect to total mesh size and the intersection algorithm (right) with respect to the size of the component mesh.}
    \label{fig:cube_speed}
\end{figure}
